====================================
Reproducible Research Assignment 1
====================================

##Get data into R
```{r}
filename <- unzip("activity.zip")
activity <- read.csv(filename, stringsAsFactors = FALSE)
activity$date<-as.Date(activity$date)
```
##What is mean total number of steps taken per day?
```{r}
activity_rm<-activity[which(!is.na(activity$steps)),]
perday<-tapply(activity_rm$steps, activity_rm$date, sum)
hist(perday,5, main = "Total number of steps taken per day", xlab = "")
```

##Summary stats
```{r}
summary(perday)
```
##What is the average daily activity pattern?
```{r}
library(ggplot2)
library(plyr)
meanday<-ddply(activity_rm, .(interval),function(x) mean(x$steps))
colnames(meanday)[2] <- "Average_steps"
plot(y=meanday$Average_steps,x=meanday$interval, type="l", xlab="5 minute interval", 
     main="Daily activity pattern", ylab="Average number of steps")
```
##obtain max average steps
```{r}
meanday[which (meanday$Average_steps==max(meanday$Average_steps)),]
```
##Imputing missing values
```{r}
actnomissing<-activity
meansteps<-tapply(activity_rm$steps, activity_rm$interval, mean)
actnomissing[which(is.na(actnomissing$steps)),1]<-meansteps[as.character(actnomissing[which(is.na(actnomissing$steps)),3])]
#Graph and compare
perday2<-tapply(actnomissing$steps, actnomissing$date, sum)
par(mfrow=c(1,2))
hist(perday,5, main = "No data adjustment", xlab = "")
hist(perday,5, main = "NA replaced with mean value", xlab = "")
```

##Summary stats for data with NA values
```{r}
summary(perday)
```
##Summary stats for data with NA values replaced with mean
```{r}
summary(perday2)
```
##Are there differences in activity patterns between weekdays and weekends?
```{r}
actnomissing$weekday<-as.character(weekdays(actnomissing$date, abbreviate = FALSE))
actnomissing$wkday[actnomissing$weekday == "Monday"] <- "Weekday"
actnomissing$wkday[actnomissing$weekday == "Tuesday"] <- "Weekday"
actnomissing$wkday[actnomissing$weekday == "Wednesday"] <- "Weekday"
actnomissing$wkday[actnomissing$weekday == "Thursday"] <- "Weekday"
actnomissing$wkday[actnomissing$weekday == "Friday"] <- "Weekday"
actnomissing$wkday[actnomissing$weekday == "Saturday"] <- "Weekend"
actnomissing$wkday[actnomissing$weekday == "Sunday"] <- "Weekend"
library(dplyr)
weekday<-filter(actnomissing,wkday=="Weekday")
weekend<-filter(actnomissing,wkday=="Weekend")
weekdaymean<-tapply(weekday$steps, weekday$interval, mean)
weekendmean<-tapply(weekend$steps, weekend$interval, mean)

plot(y=weekdaymean,x=names(weekdaymean), type="l", xlab="5 minute interval", 
     main="Weekday", ylab="Average number of steps")
plot(y=weekendmean,x=names(weekendmean), type="l", xlab="5 minute interval", 
     main="Weekend", ylab="Average number of steps")
```